Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado

### 2017-04-03 Documents/Euler/Benchmarks1D/draft.tex
formatting fixes on test 11

>>>>

Subsequent runs of this test varied the values of $\beta_{\mbox{\tiny TVB}}$ and $\beta_{\mbox{\tiny TVD}}$, while maintaining the third order method. Lower values of $\beta_{\mbox{\tiny TVB}}$ give more accurate results, with fewer, smaller oscillations appearing. Variations in $\beta_{\mbox{\tiny TVD}}$ have some effect, but not a great one. A few of the oscillations appear larger with $\beta_{\mbox{\tiny TVD}}$ set to 1.0, but the difference is not especially large.

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{11_300zoom.png}	
	\begin{tabular}{cc}
     \includegraphics[width=.475\textwidth]{11_1zoom.png}
     \includegraphics[width=.475\textwidth]{11_2zoom.png}	
    \end{tabular}
  \end{center}
  \caption{Zoomed results for test 11 at $t=1$, computed with 400 cells and the third order method. The top panel shows results when $\beta_{\mbox{\tiny TVB}}$ is set to 300, with varying values of $\beta_{\mbox{\tiny TVD}}$: 1.0 (dotted blue), 1.5 (dashed green) and 2.0 (solid red). The bottom two panels show results when $\beta_{\mbox{\tiny TVD}}$ is held constant, with varying values of $\beta_{\mbox{\tiny TVB}}$: 0 (solid red), 10 (dashed green), 50 (dotted blue), and 300 (dash-dotted pink). $\beta_{\mbox{\tiny TVD}}$ is set to 1.0 in the right panel and 2.0 in the left panel.}
\end{figure}
\clearpage
